
\begin{thebibliography}{5}

\bibitem{richard}
Richard Stallman,  Roland Pesch, Stan Shebs, et al.
\newblock {\em Debugging with GDB--The GNU Source-Level Debugger, Ninth Edition}.
\newblock Free Software Foundation, ISBN: 1-882114-77-9, Boston, USA, 2006.

\bibitem{john}
John Gilmore, Cygnus Solutions, Stan Shebs.
\newblock {\em GDB Internals--A guide to the internals of the GNU debugger}.
\newblock Free Software Foundation.

\bibitem{mips1}
Dominic Sweetman.
\newblock {\em See MIPS Run}.
\newblock Morgan Kaufmann Publishers Inc., ISBN: 1-55860-410-3, San Fransisco, USA, 1999.

\bibitem{remote1}
Bill Gatliff.
\newblock {\em Embedding with GNU: GNU Debugger}.
\newblock Embedded Systems Programming, September, 1999.

\bibitem{remote2}
Bill Gatliff.
\newblock {\em Embedding with GNU: the gdb Remote Serial Protocol}.
\newblock Embedded Systems Programming, November, 1999.

\bibitem{cstd}
ISO, IEC, ANSI, ITI.
\newblock {\em Programming Languages -- C}.
\newblock American National Standards Institute, ISO/IEC 9899:1999(E), New York, USA, 1999.

\bibitem{bfd1}
Steve Chamberlain, Cygnus Support
\newblock {\em LIB BFD, the Binary File Descriptor Library}.
\newblock Free Software Foundation.

\bibitem{chen1}
陈文平.
\newblock {\em GNU as~的移植}.
\newblock 计算机工程, 第29卷, 第10期, 2003.

\bibitem{chen2}
陈建智.
\newblock {\em Binary Utilities Generator for Application Specific Instruction Processor}.
\newblock 台湾大学资讯工程学研究所硕士学位论文, ~台湾大学图书馆, ~系统识别号: U0001-1307200517170400, 2005.

\end{thebibliography}
